Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-17 paper/manuscript.tex
Updates from Overleaf

    \caption{\textbf{Thermodynamic cycle required for an aboslute free energy calculation}}

>>>>

    \caption{\textbf{Thermodynamic cycle required for an aboslute free energy calculation.} The fully interacting ligand in water (\textbf{A}), has its charges turned off to pass to \textbf{B} followed by turning of van der Waals terms, resulting in a non-interacting ligand in water in \textbf{C}. Restraints are used on the fully interacting ligand in the binding site of a protein or host molecule \textbf{D}. The next step is to turn off the charges again (\textbf{E}) followed by the van der Waals interactions resulting in a non-interacting complex state (\textbf{F}). Free energyes can be computed as $\Delta G_{bind} = (\Delta G^{\mathrm{elec}}_{\mathrm{solv}}+ \Delta G^{\mathrm{VdW}}_{\mathrm{solv}})-(\Delta G^{\mathrm{elec}}_{\mathrm{bound}}+ \Delta G^{\mathrm{VdW}}_{\mathrm{bound}}$)
